sparqldsl
=========

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

A SPARQL DSL

## Install

Development version

```{r eval=FALSE}
devtools::install_github("ropenscilabs/sparqldsl")
```

```{r}
library("sparqldsl")
```

For examples we'll use DBpedia

## ask

```{r}
sparql_dsl("http://dbpedia.org/sparql") %>% ask(s, p, o)
```

## select

```{r}
sparql_dsl("http://dbpedia.org/sparql") %>%
  select() %>%
  where(s, p, o) %>%
  limit(10)
```

## Open citations methods

```{r}
oc_doi2ids("10.1097/igc.0000000000000609")
oc_pmid2ids("26645990")
oc_pmcid2ids("PMC4679344")
```

## Meta

* Please [report any issues or bugs](https://github.com/ropenscilabs/sparqldsl/issues)
* License: MIT
* Get citation information for `sparqldsl` in R doing `citation(package = 'sparqldsl')`
* Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
